\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-08-24 notes/2loopNLSM.tex
Sprused up some of the tikz code, put together some diagrams for the YM section.

\documentclass[11pt,letter]{article}
\pdfoutput=1
\usepackage{jheppub}
\usepackage{amsmath,amssymb}
\usepackage[dvipsnames]{xcolor}
%\usepackage{hyperref}
\usepackage{xspace}
\usepackage{ifdraft}
\usepackage{epstopdf}
\usepackage{slashed}
\usepackage{anyfontsize}
\usepackage{tocloft}
\renewcommand{\cftdot}{.}
\renewcommand{\cftsubsecleader}{\cftdotfill{\cftdotsep}}
\usepackage{diagbox}
\usepackage{colortbl}
\usepackage{bbold}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{stackengine}
\usepackage{cleveref}

@@

In our labeling of the two loop Jacobi-basis diagrams, shown in
\ace{Figure out fig}, we find that the power counting bound proposed
by Bern, Davies, and Nohle leads to an initial ansatz with 10,000
terms in the double-box, and 9849 terms for the penta-triangle.
However, recent work by Ben-Shahar, Garozzo, and Johansson
\cite{Ben-Shahar:2022ixa} \ace{Are there other good examples?}
demonstrates that constructing Feynman rules that produce manifestly
color-dual numerators for the NMHV sector of Yang--Mills requires
introducing additional auxiliary fields, including higher-spin modes,
which could shift the expected power counting in non-trivial ways.  We
therefore attempt to find an off-shell color-dual Yang--Mills
representation in which all power counting restrictions are lifted.

Without power counting restrictions, both the double-box and the
penta-triangle ansatz have an initial ansatz with 10,010 terms each.
Imposing diagram automorphisms on the two basis diagrams, we reduce
the number of terms to XX.  Gauge invariance on support of the maximal
cuts of the basis diagrams further reduces the remaining freedom to
YY.  The power-counting restriction of BDN would reduce this count to
ZZ.  In the original BDN work, they imposed three spanning generalized
unitarity cuts, shown in [].  Instead of directly imposing the
spanning cuts, we proceed with the relaxed version of the method of
maximal cuts used above in the pion construction [\ace{is James going
  to talk about something along this line in the pions section?}].  We
find that even with the completely generic ansatz, the representation
fails to satisfy the next-to-next-to-maximal cut shown in [].
Notably, imposing the BDN power-counting constraints additionally
causes a discrepancy with the N$^2$-max cuts show in [].

>>>>

\documentclass[11pt,letter]{article}
\pdfoutput=1
\usepackage{jheppub}
\usepackage{amsmath,amssymb}
\usepackage[dvipsnames]{xcolor}
%\usepackage{hyperref}
\usepackage{xspace}
\usepackage{ifdraft}
\usepackage{epstopdf}
\usepackage{slashed}
\usepackage{anyfontsize}
\usepackage{tocloft}
\renewcommand{\cftdot}{.}
\renewcommand{\cftsubsecleader}{\cftdotfill{\cftdotsep}}
\usepackage{diagbox}
\usepackage{colortbl}
\usepackage{bbold}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{stackengine}
\usepackage{subcaption}
\usepackage{cleveref}

@@

In our labeling of the two loop Jacobi-basis diagrams, shown in
\ace{Figure out fig}, we find that the power counting bound proposed
by Bern, Davies, and Nohle leads to an initial ansatz with 10,000
terms in the double-box, and 9849 terms for the penta-triangle.
Without power counting restrictions, both the double-box and the
penta-triangle ansatz have an ansatz with 10,010 terms each.  Imposing
diagram automorphisms and maximal-cut gauge invariance on the two
basis diagrams, we reduce the number of terms to XX for the
double-box, and YY for the penta-triangle.  The power-counting
restriction of BDN would further reduce these counts to 2232 and 4072.
In Ref.~\cite{Bern:2015ooa}, the unitarity matching constraints were
imposed using a spanning set of minimal physical cuts, shown in
\cref{fig:ym-spanning}.  Instead of also directly going to the
spanning cuts, we work within the framework of the Method of Maximal
Cuts \citepls{} in order to identify the simplest cut that is in
tension with the kinematic Jacobi relations.

\begin{figure}
  \begin{center}
    \begin{subfigure}{0.3\textwidth}
      \begin{center}
        \LMCut
      \end{center}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
      \begin{center}
        \PhysicalCutOne{}{}{}{}
      \end{center}
    \end{subfigure}
    \begin{subfigure}{0.3\textwidth}
      \begin{center}
        \PhysicalCutTwo{}{}{}{}
      \end{center}
    \end{subfigure}
  \end{center}
  \caption{The three spanning physical unitarity cuts of pure
    Yang--Mills at 2 loops}
  \label{fig:ym-spanning}
\end{figure}

we proceed with the relaxed version of the method of
maximal cuts used above in the pion construction [\ace{is James going
  to talk about something along this line in the pions section?}].  We
find that even with the completely generic ansatz, the representation
fails to satisfy the next-to-next-to-maximal cut shown in [].
Notably, imposing the BDN power-counting constraints additionally
causes a discrepancy with the N$^2$-max cuts show in [].

\KissingTriangles
